The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2019-04-05 pkg/partykit/inst/guideliketest/draft/draft.Rnw
results of extended simulation for stump scenario and adaptions in loading the corresponding data in the draft
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2514 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 4d4d6abb0b2f5796f73c3626d6d6dcf2f04838fe

\begin{figure}%%[t]
\setkeys{Gin}{width=\linewidth}
<<contbeta, fig=TRUE, echo=FALSE, height=4, width=8>>=
load("../sim/simres20181122_stump.rda")
sim_stump_cont <- simres$res
subdata <- subset(sim_stump_cont, test %in% c("ctree", "ctree_max","mfluc", "guide_sum_1_cor","guide_sum_12"))
#subdata <- subset(subdata, delta %in% c(0, 0.1, 0.2, 0.3, 0.4, 0.5))
subdata$test <- factor(subdata$test, 
                       levels = c("ctree", "ctree_max","mfluc", "guide_sum_1_cor","guide_sum_12"),
                       labels = c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores"))
par.settings <- list(superpose.symbol = list(col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")], 
                                             fill = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")]), 
                     superpose.line = list(col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")]))

xyplot(prop_Tsplit ~ delta | vary_beta, groups = ~ test, 
       data = subdata, 
       subset = binary_beta == FALSE & binary_regressor == FALSE & 
         only_intercept == FALSE, 
       #xlim = c(0,0.1,0.5),
       type = "l", 
       layout= c(3,1),
       lwd = 2,
       key =  list(text = list(levels(subdata$test)),
                   lines = list(lty = c(1,1,1,1,1), 
                                type = "l", 
                                col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")], 
                                lwd = 2)), 
       xlab = expression(delta),
       ylab = expression("Proportion of selecting"~Z[1]),
       index.cond = list(c(2,3,1)),
       strip = strip.custom(factor.levels = c(expression("vary "~beta[0]~" and "~beta[1]),
                                              expression("vary "~beta[0]), 
                                              expression("vary "~beta[1])),
                                    bg = "gray90"),
       par.settings = par.settings)
@
\caption{\label{fig:stump_contbeta}
Proportion of cases where the true split variable $Z_1$ is
selected over increasing effect size $\delta$ (100 data sets of 250 observations per step)
with the varying coefficient(s) being continuous. 
Each panel represents one scenario for the coefficients: 
varying intercept $\beta_0$ (left), varying slope parameter $\beta_1$ (middle) and 
both coefficients varying (right). The performances of five testing strategies are compared: 
CTree, CTree\_max, MOB, GUIDE, GUIDE\_scores.}
\end{figure}

>>>>

\begin{figure}%%[t]
\setkeys{Gin}{width=\linewidth}
<<contbeta, fig=TRUE, echo=FALSE, height=4, width=8>>=
subdata <- subset(sim_stump, test %in% c("ctree", "ctree_max","mfluc", "guide_sum_1_cor","guide_sum_12"))
#subdata <- subset(subdata, delta %in% c(0, 0.1, 0.2, 0.3, 0.4, 0.5))
subdata$test <- factor(subdata$test, 
                       levels = c("ctree", "ctree_max","mfluc", "guide_sum_1_cor","guide_sum_12"),
                       labels = c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores"))
par.settings <- list(superpose.symbol = list(col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")], 
                                             fill = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")]), 
                     superpose.line = list(col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")]))

xyplot(prop_Tsplit ~ delta | vary_beta, groups = ~ test, 
       data = subdata, 
       subset = binary_beta == FALSE & binary_regressor == FALSE & 
         only_intercept == FALSE, 
       scales=list(x=list(at=seq(1,11,2))),
       type = "l", 
       layout= c(3,1),
       lwd = 2,
       key =  list(text = list(levels(subdata$test)),
                   lines = list(lty = c(1,1,1,1,1), 
                                type = "l", 
                                col = pal[c("CTree","CTree_max","MOB", "GUIDE","GUIDE_scores")], 
                                lwd = 2)), 
       xlab = expression(delta),
       ylab = expression("Proportion of selecting"~Z[1]),
       index.cond = list(c(2,3,1)),
       strip = strip.custom(factor.levels = c(expression("vary "~beta[0]~" and "~beta[1]),
                                              expression("vary "~beta[0]), 
                                              expression("vary "~beta[1])),
                                    bg = "gray90"),
       par.settings = par.settings)
@
\caption{\label{fig:stump_contbeta}
Proportion of cases where the true split variable $Z_1$ is
selected over increasing effect size $\delta$ (100 data sets of 250 observations per step)
with the varying coefficient(s) being continuous. 
Each panel represents one scenario for the coefficients: 
varying intercept $\beta_0$ (left), varying slope parameter $\beta_1$ (middle) and 
both coefficients varying (right). The performances of five testing strategies are compared: 
CTree, CTree\_max, MOB, GUIDE, GUIDE\_scores.}
\end{figure}
